---
title: "hw02-donggyun-kim"
author: "Donggyun Kim"
date: "9/28/2017"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## 1) Create a data dictionary
[A data dictionary](https://github.com/dgyunkim/stat133-hws-fall17/blob/master/hw02/data/nba2017-player-statistics-dictionary.md)

## 2) Import the data in R
- Import data with "base"
```{r}
setwd("~/Desktop/STAT 133/stat133-hws-fall17/hw02/data")
nba2017 <- read.csv("nba2017-player-statistics.csv", 
                colClasses = c("character", "character", "factor", "character", "double", rep("integer", 19)))
str(nba2017)
```

- Import data with "readr"
`r library(readr)`
```{r}
setwd("~/Desktop/STAT 133/stat133-hws-fall17/hw02/data")
nba2017 <- read_csv("nba2017-player-statistics.csv", 
                          col_types = list(Position = col_factor(c("C", "PF", "SF", "PG", "SG"))))
str(nba2017)
```

## 3) Right after importing the data
- Process on the column "Experience"
```{r}
nba2017[["Experience"]][nba2017[["Experience"]] == "R"] <- "0"
nba2017$Experience <- as.integer(nba2017$Experience)
nba2017
```

## 4) Performance of players
- Add new variables
```{r}
nba2017$Missed_FG <- nba2017$FGA - nba2017$FGM
nba2017$Missed_FT <- nba2017$FTA - nba2017$FTM
nba2017$PTS <- nba2017$FGM + nba2017$FTM
nba2017$REB <- nba2017$OREB + nba2017$DREB
nba2017$MPG <- nba2017$MIN / nba2017$GP
```

- Calculate and add EFF
```{r}
nba2017$EFF <- (nba2017$PTS + nba2017$REB + nba2017$AST + nba2017$STL
                + nba2017$BLK - nba2017$Missed_FG - nba2017$Missed_FT - nba2017$TO) / nba2017$GP
```

- Summary of EFF
```{r}
summary(nba2017$EFF)
```

- Histogram of Efficiency (EFF)
```{r}
hist(nba2017$EFF, main = "Histogram of Efficiency (EFF)", xlab = "EFF", col = "Blue")
```

- Display the player name, team, salary, and EFF value of the top-10 players by EFF in
decreasing order
`r library(dplyr)`
```{r}
head(arrange(select(nba2017, Player, Team, Salary, EFF), desc(EFF)), 10)
```

- Provide the names of the players that have a negative EFF
```{r}
select(filter(nba2017, EFF < 0), Player)
```

- Use the function cor() to compute the correlation coefficients between EFF and all the
variables used in the EFF formula
```{r}
cor_PTS <- cor(nba2017$EFF, nba2017$PTS)
cor_REB <- cor(nba2017$EFF, nba2017$REB)
cor_AST <- cor(nba2017$EFF, nba2017$AST)
cor_STL <- cor(nba2017$EFF, nba2017$STL)
cor_BLK <- cor(nba2017$EFF, nba2017$BLK)
cor_MFG <- cor(nba2017$EFF, -nba2017$Missed_FG)
cor_MFT <- cor(nba2017$EFF, -nba2017$Missed_FT)
cor_TO <- cor(nba2017$EFF, -nba2017$TO)
```

- Display the computed correlations in descending order, either in a vector or a data
frame.
```{r}
corrs <- c(cor_PTS, cor_REB, cor_AST, cor_STL, cor_BLK, cor_MFG, cor_MFT, cor_TO)
mydat <- data.frame(corrs)
arrange(mydat, desc(corrs))
```

- create a barchart with the correlations
`r library(ggplot2)`
```{r}
barplot(sort(corrs, decreasing = TRUE), main = "Correlations between Player Stats and EFF",
        names.arg = c("PTS", "REB", "AST", "STL","BLK", "Missed_FT", "Missed_FG", "TO"),
        cex.names = 0.6, col = ifelse(corrs > 0, "blue", "red"), ylim = c(-1, 1))
abline(h = 0, lwd = 2)
```

## 5) Efficiency and Salary
- scatterplot between Efficiency and Salary
```{r}
plot(nba2017$EFF, nba2017$Salary, main = "Scatterplot between Efficiency and Salary",
     xlab = "EFF", ylab = "Salary", pch = 21, cex = 1.5, col = "skyblue", bg = "red",
     cex.lab = 1.5)
lines(lowess(nba2017$EFF, nba2017$Salary), lwd = 3, col = "green")
text(x = 20, y = 2.0e+07, labels = "Lowess", cex = 1.5, col = "green")
```

- the linear correlation coefficient between Efficiency and Salary
```{r}
b1 <- cor(nba2017$EFF, nba2017$Salary)*sd(nba2017$Salary)/sd(nba2017$EFF)
b0 <- mean(nba2017$Salary) - b1*mean(nba2017$EFF)
y_hat <- b0 + b1*nba2017$EFF
RSS <- sum((nba2017$Salary - y_hat)^2)
TSS <- sum((nba2017$Salary - mean(nba2017$Salary)^2))
cor_coeff <- 1 - RSS/TSS
cor_coeff
```

- Create a data frame players2
```{r}
players2 <- select(filter(nba2017, MPG >= 20), Player, MPG, EFF, Salary)
players2
```

- Use this data frame to create a scatterplot between Efficiency and Salary
```{r}
plot(players2$EFF, players2$Salary, main = "Scatterplot between Efficiency and Salary",
     xlab = "EFF", ylab = "Salary", cex = 1.5, cex.lab = 1.5, pch = 21, col = "yellow", 
     bg = "pink")
lines(lowess(players2$EFF, players2$Salary), lwd = 3, col = "blue")
text(x = 20, y = 1.7e+07, labels = "Lowess", cex = 1.5, col = "blue")
```

- Compute the linear correlation coefficient
```{r}
b1 <- cor(players2$EFF, players2$Salary)*sd(players2$Salary)/sd(players2$EFF)
b0 <- mean(players2$Salary) - b1*mean(players2$EFF)
y_hat <- b0 + b1*players2$EFF
RSS <- sum((players2$Salary - y_hat)^2)
TSS <- sum((players2$Salary - mean(players2$Salary)^2))
cor_coeff <- 1 - RSS/TSS
cor_coeff
```

