---
title: "Untitled"
author: "Donggyun Kim"
date: "10/12/2017"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Lab 7: Simple Functions and Conditionals   
    
Simple math functions
```{r}
f <- function(x){
  x*x
}
g <- function(x){
  2*x + 5
}
```

Test functions
```{r}
f(2)
f(-5)

g(0)
g(-5/2)
```

Composite functions
```{r}
fog <- function(x){
  f(g(x))
}
gof <- function(x){
  g(f(x))
}
```

Test functions
```{r}
fog(2)
fog(-5)

gof(0)
gof(-5/2)
```

Pythagoras
```{r}
pythagoras <- function(a, b){
  sqrt(a^2 + b^2)
}
```

Test
```{r}
pythagoras(3, 4)
```

Modify the function
```{r}
pythagoras <- function(a, b = a){
  sqrt(a^2 + b^2)
}
```

Test
```{r}
pythagoras(5)
```

Unit conversion formulas
```{r}
miles2kms <- function(x){
  1.6*x
}
```

Table for miles and kms
```{r}
miles <- c(seq(1, 10, 1), seq(10, 100, 10))
mydat <- data.frame(list(
  miles = miles
))
mydat$kms <- miles2kms(miles)
mydat
```

Gallons to liters
```{r}
gallon2liters <- function(x){
  3.78541*x
}
liters2gallon <- function(x){
  x*x/gallon2liters(x)
}
```

Table for liters and gallons
```{r}
liters <- c(seq(1, 10, 1), seq(10, 100, 10))
gallons <- liters2gallon(liters)
mydat2 <- data.frame(list(
  liters = liters, 
  gallons = gallons  
))
mydat2
```

Seconds to years
```{r}
seconds2years <- function(x){
  x/60/60/24/365
}
seconds2years(10^9)
```

Gaussian function
```{r}
gaussian <- function(x, m, s){
  exp(-((x - m)/s)^2/2)/(s*sqrt(2*pi))
}
gaussian(1, 0, 2)
dnorm(1, 0, 2)
```

Plot Gaussian function
```{r}
x_values <- seq(-4.5, 4.5, 0.1)
y_values <- gaussian(x_values, 0, 2)
plot(x_values, y_values, las = 1, type = "l", lwd = 2)
```

Polynomial function
```{r}
poly1 <- function(x){
  x^3
}
poly2 <- function(x){
  (x^2-1)*(x+3)^3
}
poly3 <- function(x){
  (x^2-1)*(x^2-9)
}
```

Plot polynomial
```{r}
x <- seq(-4, 4, length.out = 20)
y1 <- poly1(x)
y2 <- poly2(x)
y3 <- poly3(x)

plot(x, y1, type = 'l', lwd = 3, col = "red", las = 1)
abline(h = 0, v = 0, col = "gray", lwd = 1.5)
title(main = expression(paste(f(x), ' = ', x^3)))

plot(x, y2, type = "l", lwd = 3, col = "red", las = 1, 
     main = expression(paste(f(x), " = ", (x^2 - 1), (x + 3)^3)))
abline(h = 0, v = 0, col = "gray", lwd = 1.5)

plot(x, y3, type = "l", lwd = 3, col = "red", las = 1)
abline(h = 0, v = 0, col = "gray", lwd = 1.5)
title(main = expression(paste(f(x), " = ", (x^2 - 1), (x^2 - 9))))
```

Descriptive statistics
```{r}
descriptive <- function(x){
  sm <- summary(x)
  min <- sm[1]
  q1 <- sm[2]
  median <- sm[3]
  mean <- sm[4]
  q3 <- sm[5]
  max <- sm[6]
  range <- max - min
  iqr = IQR(x)
  sd = sd(x)
}
```

Binomial function
```{r}
combinations <- function(n, k){
  factorial(n)/factorial(k)/factorial(n-k)
}
combinations(n = 5, k = 2)

binom_prob <- function(n, k, prob){
  combinations(n, k)*prob^k*(1 - prob)^(n - k)
}
binom_prob(n = 5, k = 2, prob = 0.5)
```

Use binom_prob() to obtain the probability of getting more than 3 heads     
in 5 tosses with a biased coin of 35% chance of heads.
```{r}
myprob <- binom_prob(n = 5, k = 3:5, prob = 0.35)
sum(myprob)
```

Consider rolling a fair die 10 times.     
Use binom_prob() to find the probability of getting exactly 3 sixes?
```{r}
myprob2 <- binom_prob(n = 10, k = 3, prob = 1/6)
myprob2
```

If conditionals
```{r}
z <- 100*pi
if (z > 100){
  z <- 100
} else if (z < 0){
  z <- 0
} else {
  z
}
```

Even number
```{r}
is_even <- function(x) {
  if ((x %% 2) == 0) {
    TRUE
  } else if ((x %% 2) == 1) {
    FALSE
  } else {
    NA
  }
}
is_even(10)
is_even(33)

```

Odd number
```{r}
is_odd <- function(x){
  if (is_even(x) == FALSE ) {
    TRUE
  } else if (is_even(x) == TRUE) {
    FALSE
  } else {
    NA
  }
}
is_odd(1)
is_odd(4)

```

Switch
```{r}
grade <- function(score){
  if (score <= 100 & score >= 90) {
    "A"
  } else if (score < 90 & score >= 80) {
    "B"
  } else if (score < 80 & score >= 70) {
    "C"
  } else if (score < 70 & score >= 60) {
    "D"
  } else if (score < 60) {
    "F"
  } else {
    stop("score must be a number between 0 and 100")
  }
}
grade(score = 90)
grade(score = 89.9999)
grade(score = 70.0000001)
grade(score = 50)

```

Switch function
```{r}
miles2inches <- function(x = 1) {
  63360*x
}
miles2feet <- function(x = 1) {
  5280*x
}
miles2yards <- function(x = 1) {
  1760*x
}
miles2meters <- function(x = 1) {
  0.00062137*x
}
miles2kms <- function(x = 1) {
  0.62137*x
}
miles2inches(2)
miles2feet(2)
miles2yards(2)
miles2meters(2)
miles2kms(2)
```

Using switch()
```{r}
convert <- function(x, to = "km") {
  switch(to,
         "in" = miles2inches(x),
         "ft" = miles2feet(x),
         "yd" = miles2yards(x),
         "m" = miles2meters(x),
         "km" = miles2kms(x))
}
convert(3, "in")
convert(3, "ft")
convert(3, "yd")
convert(3, "m")
convert(3, "km")
convert(3)
```


