---
title: "hw01-donggyun-kim"
author: "Donggyun Kim"
date: "9/21/2017"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. A bit of data preprocessing
## + Importing the data
```{r}
load("data/nba2017-salary-points.RData")
```

## + Showing the list
```{r}
ls()
```

## + Creating a **_new_** salary variable
```{r}
new_salary <- salary/1000000

round(new_salary, digits=2)
```

## + Creating a **_new_** exprience variable
```{r}
new_experience <- strtoi(experience, base = 0L)
new_experience[is.na(new_experience)] <- 0

new_experience
```

## + Replacing old level to new level and creating a **_new_** position variable
```{r}
position <- replace(position, position == 'C', 'center')
position <- replace(position, position == 'SF', 'small_fwd')
position <- replace(position, position == 'PF', 'power_fwd')
position <- replace(position, position == 'SG', 'shoot_guard')
position <- replace(position, position == 'PG', 'point_guard')

new_position <- factor(position)
table(new_position)
```

# 2. Scatterplot of Points and Salary
```{r}
plot(points, new_salary, main = "Scatterplot of Points and Salary", 
     col = "blue", xlab = "Points", ylab = "Salary (in millions)", 
     cex = 1, cex.lab = 1.5, cex.main = 2.0, pch = 21, bg = "green")
```

# 3. Correlation between Points and Salary
## + Number of individuals
```{r}
n <- length(player)
n
```

## + Mean of variable X (Points)
```{r}
xbar <- sum(points)/n
xbar
```

## + Mean of variable Y (Salary)
```{r}
ybar <- sum(new_salary)/n
ybar
```

## + Variance of X (Points)
```{r}
var_x <- sum((points-xbar)^2)/(n-1)
var_x
```

## + Variance of Y (Salary)
```{r}
var_y <- sum((new_salary-ybar)^2)/(n-1)
var_y
```

## + Standard deviation of X (Points)
```{r}
sd_x <- sqrt(var_x)
sd_x
```

## + Standard deviation of Y (Salary)
```{r}
sd_y <- sqrt(var_y)
sd_y
```

## + Covariance between X and Y
```{r}
cov_xy <- sum((points - xbar)*(new_salary - ybar))/(n-1)
cov_xy
```

## + Correlation between X and Y
```{r}
cor_xy <- cov_xy/(sd_x*sd_y)
cor_xy
```

# 4. Simple Linear Regression
```{r}
b1 <-  cor_xy*sd_y/sd_x
b0 <-  ybar - b1*xbar
y_hat <- b0 + b1 * points

```

## + Summary statistics of y_hat
```{r}
summary(y_hat)
```

## + The regression equation
\[
 \hat{Y} = b_0 + b_1 \times X
\]

## + The slope of coefficient b1
The slope b1 equals covariance between X and Y divided by variance of X 
```{r}
b1
```
```{r}
cov_xy / var_x

```

## + The intercept term b0
```{r}

```

## + the predicted salary
```{r}
predictied_salary <- function(x){
  y <- b0 + b1 * x
  return(y)
}
```
### A player who scores 0 point would get
```{r}
predictied_salary(0)
```
### A player who scores 100 points would get
```{r}
predictied_salary(100)
```
### A player who scores 500 points would get
```{r}
predictied_salary(500)
```
### A player who scores 1000 points would get
```{r}
predictied_salary(1000)
```
### A player who scores 2000 points would get
```{r}
predictied_salary(2000)
```

# 5. Plotting the regression line
```{r}
plot(points, new_salary, main = "Regression and Lowess lines", 
     col = "red", xlab = "Points", ylab = "Salary (in millions)", 
     cex = 1, cex.lab = 1.5, cex.main = 2.0, pch = 21, bg = "blue")
abline(a = b0, b = b1, lwd = 3, col = "Skyblue")
lines(lowess(points, new_salary), lwd = 3, col = "Pink")
text(x = 2400, y = 30, labels = "Lowess", col = "Pink")
text(x = 2400, y = 19, labels = "Regression", col = "Skyblue")
```

# 6. Regression residuals and Coefficient of Determination R-squared

## + The vector of residuals
```{r/}
residuals <-  new_salary - y_hat
summary(residuals)
```

## + The ReSidual Sum of Squares
```{r}
RSS <- sum(residuals^2)
RSS
```

## + The Total Sum of Squares
```{r}
TSS <- sum((new_salary - ybar)^2)
TSS
```

## + The coefficient of determination R-squared
```{r}
R_sqrd <- 1 - RSS/TSS
R_sqrd
```

# 7. Exploring Position and Experience
```{r}
plot(x = new_experience, y = new_salary, main = "Scatterplot with lowess smooth", 
     xlab = "Years of Experience", ylab = "Salary (in millions)", 
     cex = 1.5, cex.main = 2, cex.lab = 1.5, cex.axis = 1.5, pch = 21, bg = "Gray")
lines(lowess(new_experience, new_salary), lwd = 3.5, col = "Red") 


scatterplot3d::scatterplot3d(points, new_experience, new_salary, main = "3D Scatterplot",
              xlab = "Points", ylab = "Experience", zlab = "Salary", cex.axis = 1.5, cex.lab = 1.5)

boxplot(new_salary[new_position == 'center'], new_salary[new_position == 'power_fwd'],
        new_salary[new_position == 'small_fwd'], new_salary[new_position == 'point_guard'],
        new_salary[new_position == 'shoot_guard'], ylab = 'Salary (in millions)', xlab = 'Position',
        names=c("center", "power_fwd", "small_fwd", "point_guard", "shoot_guard"))


```

## + Provide concise descriptions for the plots of this section.
Plots help to analyze and understand data sets

## + From the scatterplots, does Experience seem to be related with Salary?
No, lowess line shows that Experience is not realated with Salary.

## + From the boxplot, does Position seem to be related with Salary?
No, Position does not seem to be related with Salary.

# 8. Comments and Reflections
+ What was easy(-ish) even though we haven’t done it in class?  
Part 3) Correlation
+ How much time did it take to complete this HW?  
8 hours  
+ What was the most time consuming part?  
Data processing  
+ Was there anything that you did not understand? or fully grasped?  
Wirting equation using inline code  
+ Was there anything frustrating in particular?  
I could never find how to write equation by inline code. 
+ Was there anything exciting? Something that you feel proud of?  
Using 'sum()' function and number of samples to find mean, variance instead of using 'mean()' and 'var()' functions